Figures for conference paper

### 2019-04-25 conference figures.Rmd
CV figure

load("Output/_catalogues_tmp_topic_model_tibble.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")

@@

@@

>>>>

load("Output/_catalogues_tmp_topic_model_tibble.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")

@@

# Model Selection (topic model)

```{r}
df_logLike_catalogue %>%
  ggplot(aes(x = n_topic, y = LogLikelihood)) +
  geom_vline(xintercept = 80, col = "red", alpha = 0.5, linetype = "dashed") +
  geom_line() +

  labs(title = "Model Selection", subtitle = "The maximum-likelihood model has 80 topics", x = "Number of Topics", y = "Log-Likelihood") +

  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
         width = plot_width, height = plot_height)
```

@@

# CV
```{r}
fit_lasso %>%
  ggplot(aes(y = cv_error, group = 1)) +
  geom_boxplot() +
  theme(axis.ticks.x = element_line(color = "white"),
        axis.text.x = element_text(color = "white"),
        panel.border = element_rect(color = "white"),
        panel.grid = element_line(color = "white")
        ) +

  labs(title = "Distribution of Prediction Error", y = "Cross-Validation \n Mean Absolute Error")

ggsave(filename = str_c("CV.jpeg"), path = output_folder,
         width = plot_width/1.9, height = plot_height/1.2)

fit_lasso %>%
  summarize(Mean = mean(cv_error),
            `Weighted mean` = weighted.mean(cv_error, n),
            Median = median(cv_error),
            `Standard Deviation` = sd(cv_error),
            Minimum = min(cv_error),
            Maximum = max(cv_error)) %>%
  gather(key = x, value = y) %>% 
  kable("latex", booktabs = TRUE, col.names = NULL) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/CV.pdf"))
```
